NumPy---Array Programming in Python

### 2020-02-16 body.tex
Update Figs

  \caption{\textbf{NumPy API and Array Protocol.} Through its array protocol, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{mean} function is called on a Dask
     array.  The call succeeds by dispatching to the appropriate library implementation
     (i.e., Dask in this case) and results in a new Dask array.  Compare this
     code to the example code in Fig.~\ref{fig:array-concepts}g.
  }\label{fig:array-protocol}

>>>>

  \caption{\textbf{NumPy API and Array Protocols.} Through its array protocols, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{mean} function is called on a Dask
     array.  The call succeeds by dispatching to the appropriate library implementation
     (i.e., Dask in this case) and results in a new Dask array.  Compare this
     code to the example code in Fig.~\ref{fig:array-concepts}g.
  }\label{fig:array-protocol}
